---
title: "full_analysis"
author: "Dylan Glave"
date: "8/16/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)


library(tidyverse)
library(here)
library(janitor)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(knitr)
library(naniar)
library(here)
library(dplyr)
library(scales)
library(stringr)

```

## R Markdown

Here is a complete Markdown document combining work from ER, LN and DG's combined analysis on Rare's Fish Forever survey data. 


To start, we'll read in *all* relevant CSVs

```{r, echo=FALSE}
# Read in .csv from new Rare data portal
hhs_all <- read_csv(here("new_portal_data", "hh_surveys_all.csv"))

# Read in separate question .csvs from the new Rare data portal
hhs_q44 <- read_csv(here("new_portal_data", "hh_q44.csv"))
hhs_q45 <- read_csv(here("new_portal_data", "hh_q45.csv"))
hhs_q48 <- read_csv(here("new_portal_data", "hh_q48.csv"))


```


Next, we go through questions 44, 45, and 48 to remove any duplicates

We do this because, when reading in the original CSVs, we saw answers like, "Yes, Yes, Yes," "No, No, No, No, No" and "Yes male, yes Female, Unsure."

These questions ask respondents about their *household,* so it's possible that they answered individually for each member of their hosuehold. 
However, the goal of this analysis is just to see if any single member of a hosuehold participated the management meetings, or enforcement.  



```{r}
# Check dupes for all questions
dupes_44 <- data.frame(table(hhs_q44$submissionid)) %>% 
  rename(submissionid = Var1)

dupes_45 <- data.frame(table(hhs_q45$submissionid)) %>% 
  rename(submissionid = Var1)

dupes_48 <- data.frame(table(hhs_q48$submissionid)) %>% 
  rename(submissionid = Var1)
```

The chunks below use recode() to change cells within Qs 44, 45, and 48 to each have a single answer. 

```{r}
# Cleaning data
# Question 44
hhs_q44_dupes <- hhs_q44 %>% 
  inner_join(dupes_44, hhs_q44, by = "submissionid") %>% 
  arrange(desc(submissionid)) 

# Drops rows where submissionid's with a frequency greater than 1 are labeled "Not sure"
hhs_q44_dupes <- hhs_q44_dupes[!(hhs_q44_dupes$Freq > 1 & hhs_q44_dupes$`44_meeting_attendance` == "Not sure"),]

# Drops rows that have NA
hhs_q44_dupes <- hhs_q44_dupes[!(hhs_q44_dupes$`44_meeting_attendance` == "na"),] 

# Changes "No management to "No"
hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "No management" = "No"))

# Probably want to do this last
hhs_q44_dupes <- hhs_q44_dupes %>%
  group_by(submissionid, Freq) %>%
  summarise(`44_meeting_attendance` = paste(`44_meeting_attendance`, collapse = ' ')) %>% 
  select(-Freq)

# Checks to see if there are any dupes left
hhs_q44_dupes_2 <- data.frame(table(hhs_q44_dupes$submissionid)) %>% 
  rename(submissionid = Var1)

# Now recode the answer combos into Yes, No, & Not Sure only
hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "Yes female" = "Yes"))

hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "Yes male" = "Yes"))

hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "Yes male Yes female" = "Yes"))

hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "Yes female Yes male" = "Yes"))

hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "Yes male No" = "Yes"))

hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "No Yes male" = "Yes"))

hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "Yes female Yes male No" = "Yes"))

hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "No Yes female" = "Yes"))

hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "Yes female No" = "Yes"))

hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "Yes male No Yes female" = "Yes"))

hhs_q44_dupes <- hhs_q44_dupes %>%
  mutate(`44_meeting_attendance` = recode(`44_meeting_attendance`, "No No" = "No"))

```


The following chunk combines duplicated from Question 45, and renames the observations that have been repeated. 
End result: 1 observation for each submission ID

```{r}
# Question 45
hhs_q45_dupes <- hhs_q45 %>% 
  inner_join(dupes_45, hhs_q45, by = "submissionid") %>% 
  arrange(desc(submissionid)) 

# Drops rows where submissionid's with a frequency greater than 1 are labeled "Not sure"
hhs_q45_dupes <- hhs_q45_dupes[!(hhs_q45_dupes$Freq > 1 & hhs_q45_dupes$`45_leadership_position` == "Not sure"),]

# Drops rows that have NA
hhs_q45_dupes <- hhs_q45_dupes[!(hhs_q45_dupes$`45_leadership_position` == "na"),] 

# Changes "No management" option to "No"
hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "No management" = "No"))

# Probably want to do this last - Freq column here is artifact
hhs_q45_dupes <- hhs_q45_dupes %>%
  group_by(submissionid, Freq) %>%
  summarise(`45_leadership_position` = paste(`45_leadership_position`, collapse = ' ')) %>% 
  select(-Freq)

# Checks to see if there are any dupes left
hhs_q45_dupes_2 <- data.frame(table(hhs_q45_dupes$submissionid)) %>% 
  rename(submissionid = Var1)

# Now recode the answer combos into Yes, No, & Not Sure only
hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "Yes female" = "Yes"))

hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "Yes male" = "Yes"))

hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "Yes male Yes female" = "Yes"))

hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "Yes female Yes male" = "Yes"))

hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "Yes male No" = "Yes"))

hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "No Yes male" = "Yes"))

hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "No Yes female" = "Yes"))

hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "Yes female No" = "Yes"))

hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "Yes male Yes male" = "Yes"))

hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "No No No" = "No"))

hhs_q45_dupes <- hhs_q45_dupes %>%
  mutate(`45_leadership_position` = recode(`45_leadership_position`, "No No" = "No"))
```


Below, the same happens for question 48
```{r}
# Question 48 
hhs_q48_dupes <- hhs_q48 %>% 
  inner_join(dupes_48, hhs_q48, by = "submissionid") %>% 
  arrange(desc(submissionid)) 

# Drops rows where submissionid's with a frequency greater than 1 are labeled "Not sure"
hhs_q48_dupes <- hhs_q48_dupes[!(hhs_q48_dupes$Freq > 1 & hhs_q48_dupes$`48_enforcement_participation` == "Not sure"),]

# Drops rows that have NA
hhs_q48_dupes <- hhs_q48_dupes[!(hhs_q48_dupes$`48_enforcement_participation` == "na"),] 

# Changes "No management" option to "No"
hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "No management" = "No"))

# Change "No enforcement system" and "There is no enforcement system" to "No"
hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "No enforcement system" = "No"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "There is no enforcement system" = "No"))

# Probably want to do this last - Freq column here is artifact
hhs_q48_dupes <- hhs_q48_dupes %>%
  group_by(submissionid, Freq) %>%
  summarise(`48_enforcement_participation` = paste(`48_enforcement_participation`, collapse = ' ')) %>% 
  select(-Freq)

# Checks to see if there are any dupes left
hhs_q48_dupes_2 <- data.frame(table(hhs_q48_dupes$submissionid)) #%>% 
  #rename(submissionid = Var1)

# Now recode the answer combos into Yes, No, & Not Sure only
hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "Yes female" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "Yes male" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "Yes male Yes female" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "Yes female Yes male" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "Yes male No" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "No Yes male" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "No Yes female" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "Yes female No" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "No No No" = "No"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "No No" = "No"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "Yes male No No" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "No No Yes male" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "Yes female Yes female Yes female" = "Yes"))

hhs_q48_dupes <- hhs_q48_dupes %>%
  mutate(`48_enforcement_participation` = recode(`48_enforcement_participation`, "Yes female Yes male No" = "Yes"))
```


After recoding/cleaning, these different df were all combined into `hhs_complete_all` using `right_join`

```{r}
# Join the datasets after all the cleaning is done
hhs_all_48 <- right_join(hhs_q48_dupes, hhs_all, by = "submissionid")

hhs_all_45 <- right_join(hhs_q45_dupes, hhs_all_48, by = "submissionid")

hhs_all_complete <- right_join(hhs_q44_dupes, hhs_all_45, by = "submissionid")

#write.csv(hhs_all_complete, file = "hhs_all_complete.csv")

# No need to run the above code again, I have already written a .csv with the joined datasets

hhs_all_complete <- read_csv(here("new_portal_data", "hhs_all_complete.csv"))
```


Here is a quick summary table of the total number of responses, which matches the **original** number of surveys completed
17712
```{r}

# Get list of all reserves by country & how many HH surveys were answered
summary <- hhs_all_complete %>% 
  count(country, level1_name, level2_name, ma_name) %>% 
  #arrange(-n) %>% 
  mutate(level1_name = fct_reorder(country, n, sum)) %>% 
  adorn_totals("row")

# Summary table contains two NA's in the 'ma_name' column
# 75 reserves if you look at uniques
```

##### Filtering Cleaned Data

Alright! 

This marks the end of the "cleaning" data section. The final two dataframes 
(hhs_all_complete and summary) have each survey resonse as 1 row, with no duplicates, and questions that were answered multiple times (44, 45, and 48) now have 1 answer of *Yes, No,* or *Unsure*. 


```{r, include=TRUE, echo=FALSE}


```


OK! Here we have re-done all the *agreement* tables. From here, I'll do the same for engagement. I'll then hide the previous code bits in the adapted Rmd. Today, I'll also try to recode 0s and 1s. 
NOTE TO DYL: Still need to go over Indonesia numbers with TQ. 
#### Reshaping Engagement
##### Goal: Retain a robust set of answered questions, and increase N to several thousand. 


```{r}
 hhs_complete_filtered <- hhs_all_complete %>% 
  data.frame() %>% 
  clean_names() %>% 
 select( c(1:2, 6:18, 21:28, x44_meeting_attendance, x45_leadership_position,
x48_enforcement_participation,  x53_encourage_regulations,
x61f_rights_distribution_fair, x61h_individual_behavior,
           x10_mpa_important, x43_ma_benefits, x43_ma_benefits_opinion, x46_represent_interests, x47_represent_contributions, x52_ma_benefit_5yrs, x53_encourage_regulations, x61a_current_regulations, x61e_violations_decrease_profit, x62_reserve_compliance, x64_wrong_fishing_reserve,
x11a_income_farming, x11a_months_farming, x11b_income_harvesting, x11b_months_harvesting, x11c_income_fishing_artisanal,  x11c_months_fishing_artisanal, x11d_income_fishing_industrial,
x11d_months_fishing_industrial, x11e_income_buying_trading, x11e_months_buying_trading, x11f_income_processing, x11f_months_processing, x11g_income_aquaculture, x11g_months_aquaculture, x11h_income_extraction,
x11h_months_extraction, x11i_income_tourism, x11i_months_tourism,   x11j_income_other_wage, x11j_months_other_wage, x11k_income_other,
x11k_months_other, x11k_other_source, 
x12a_fishing_men, x12b_fishing_women, x12c_fishing_children, 
x19_current_fish_catch, 
x22_catch_5yrs,                   
x23_job_secure, 
x30_trust_community,x30_trust_community_neighbors, x30_trust_fishers_community,
x30_trust_fishers_other, x30_trust_local_decision,
x30_trust_ngo, x30_trust_regional_decision, x30_trust_religious_leaders,
x30_trust_village_alert, x31_my_community_ability,
x38_reserve_fishing_allowed, 
x39_ma_boundaries_aware, 
x40_reserve_boundaries_aware,
x49_enforcement_responsible,
x50_ma_punishment,
x51a_fishers_gear_not_permitted, x51b_fishers_reserves, 
x51c_fishers_ma_area, x51d_fishers_violate_fish_size, x51e_fishers_caught,
x55_worry_food, x55_worry_food,
x56_reduce_meal_size_adult,  
x60_hh_fish_consumption,
x61b_catch_recording, x61c_community_participation, x61d_strong_enforcement, 
x61h_individual_behavior,
x61i_help_neighbors,
x66_reaction_fishing_reserve, x66_response_fishing_reserve)) %>% 
 mutate_at(c(24:25), ~replace(., is.na(.), 0)) %>% 
   drop_na(24:29, 30, 31, 33:36, 38:39)


```

- *For Questions 44 and 45* 
 I used mutate_at() to change NAs to 0s. right now it may looks weird, but soon it will all be zeroes and ones. These were only asked to "fisher households" and reduce N a lot. They pair with Questions 46 and 47 (also only asked to fisher households.) 

- *Regarding Question 61e* (Violations decrease profit)
removing NA rows removes 3000 of our 3440 observations, we may just need to drop this question from the agreement index. [Talk to TQ!]

- *Dropping NAs*: We drop NAs for all* Engagement and Agreement Questions. 
*We do not drop NAs for the open-ended opinion questions, or 61e, mentioned above. 

- *For Q 46-47* we've excluded NAs since they mostly represent "non-fisher households" The difference in n goes from 5640 to ~3300. We want to see how *fishers* comply though. So the smaller N will show us that. 

Let's just make a quick table with the *counts* of all the survey responses that we have for analysis. 

```{r}
hhs_filtered_count <- hhs_complete_filtered %>% 
  count(ma_name) %>% 
  arrange(-n) %>% 
  #mutate(level1_name = fct_reorder(level1_name, n, sum)) %>% 
  adorn_totals("row") %>% 
  rename("Managed Access Area" = ma_name) %>% 
  rename("Number of surveys with all 'Agreement' and 'Engagement' questions answered" = n)


count_table <- knitr::kable(hhs_filtered_count, format = "html", caption = "Engagement and Agreement Summary") %>% 
  #column_spec(1, italic = TRUE) %>% 
  row_spec(dim(hhs_filtered_count)[1], bold = TRUE) %>%
  kable_styling(c("condensed", "responsive", "bordered"), full_width = F, position = "right") %>% 
  collapse_rows(columns = 1, valign = "middle")

count_table

```



#### Coding values to survey Answers
I'll start reassigning 0s and 1 to all the binary Questions
**This is not final** I'm exploring the methods to do this in code, next week Tasha and I will decide the actual valuation of each piece. 
Let me list out which A and E questions have binary responses, if the majority of these have "neither agree nor disagree," then I'll move from -1 to 1, with a neutral option. 


###### Engagement
Apologies for listing these so many times, that will change in the final Rmd. 
- 44: Yes/No 1/-1 (We recoded not sure to No, see Methods)
- 45: Yes/No 1/-1 (We recoded 'Not sure to No, see Methods)
- 48: Yes/No/  No enforcement 1/0/-1 


- 53: Very Often - Never, community has no fishing regulations [Flag for this being its own index]


- 61 (f): Likert Scale (Strongly) Agree-Disagree 
- 61 (g): Likert Scale (Strongly) Agree-Disagree
IS there a standard for measuring Qs against on another? Should we have our eyes out for some danger in making this index? Any ideas what could happen? 
IS -1 to 1 reasonable? What about using the likerts 
Not sure --> No. we ahve the rationale that engagement would 
"compress often and very often? 0.5 and 1?" 
generally deal with issue of likert scale, using ordinal but not implying that "very often" is 2x good. 
Watch allison ordinal 
###### Agreement 
- 10: Yes/No/Neutral 1,0,-1
- 43: Yes/No: 1, -1 (was there an Unsure answer here?)
- 46: Agree/Neutral/Disagree: 1, 0. -1
- 47: Agree/Neutral/Disagree: 1, 0. -1
- 52: Yes, No, Unsure: 1, 0,-1
- 61(a): Likert Scale (Strongly) Agree-Disagree
- 61(e): Likert Scale (Strongly) Agree-Disagree
- 62: Belief that fish catch will... Go up, Go down, remain the same, unsure. 1, 0, -1
- 64:  
For 64, which one is included, is 63 included? 
I'll start converting the "easy" questions to 1s and 0s. 
**Because there was so much much dang coding in the global_filtered, I'll make a new dataframe for the numbered version. 
We'll call it **hhs_filtered_numeric**


* Starting to recode likert scale questions into numbers*

```{r}
hhs_filtered_numeric <- hhs_complete_filtered %>% 
  mutate(x44_meeting_attendance = recode(x44_meeting_attendance, "Yes" = 1, "No"  = -1, "Not sure" = 0, "0" = 0)) %>% 
  mutate(x45_leadership_position = recode(x45_leadership_position, "Yes" = 1, "No"  = -1, "Not sure" = 0, "0" = 0)) %>% 
  mutate(x48_enforcement_participation = recode(x48_enforcement_participation, "Yes" = 1, "No"  = -1, "Not sure" = 0, "0" = 0))  %>% 
   mutate(x53_encourage_regulations = recode(x53_encourage_regulations,    "Never" = -2, "Rarely" = -1, "Sometimes" = 0,   
"Often" = 1, "Very often" = 2, "No regulations" = 0))


```



