---
title: 'Part 2: Indices and Mapping'
author: "Dylan Glave"
date: "1/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```



Loading in dataframe that I used `write.csv` to build. 
For the purpose of exhaustive reproducilibity, please run to line [LINE THAT WRITE.CSV HHS_FILTERED IS ON]  or to completion before exploring this doucment. 
Thanks for safe data science =). 
```{r}
hhs_complete_filtered <- read_csv()
```




we're adding 1 question to the Agreement index, either `x30_trust_local_decision` or `30_trust_regional_decision`

I'll run a `corplot` how the two questions compare

```{r}
x30_compared <- 
  hhs_complete_filtered %>% 
  select(x30_trust_local_decision, x30_trust_regional_decision) %>% 
  drop_na()

corrplot(cor(x30_compared))

```

alright, they're highly correlated, we're going to stick with "local decision-makers"




##### Testing our Data 


1. Confirmatory Factor Analysis

Question:

Test: 

Result: 


2. Chi-Squared testing on our different Figure data 

Are our different *categorial* variables different from one another? 

Starting with







